### 2024-10-09 README.Rmd
0.8 ready
vignette updated, figures working?

[<img src="vignettes/cols4all2.png" width="900"/>](vignettes/cols4all2.png)

@@

[<img src="vignettes/cols4all_fair_sort_cbf.png" width="900"/>](vignettes/cols4all_fair_sort_cbf.png)

@@

[<img src="vignettes/cols4all_div.png" width="900"/>](vignettes/cols4all_div.png)

@@

[<img src="vignettes/c4a_pals.png" width="900"/>](vignettes/c4a_pals.png)

@@

[<img src="vignettes/area7.png" width="900"/>](vignettes/area7.png)

@@

[<img src="vignettes/area7d.png" width="900"/>](vignettes/area7d.png)

@@

[<img src="vignettes/line7_wt.png" width="440"/>](vignettes/line7_wt.png)
[<img src="vignettes/line7_bk.png" width="440"/>](vignettes/line7_bk.png)

@@

[<img src="vignettes/friendly13.png" width="900"/>](vignettes/friendly13.png)

>>>>

[<img src="vignettes/cols4all2.jpg" width="900"/>](vignettes/cols4all2.jpg)

@@

[<img src="vignettes/cols4all_fair_sort_cbf.jpg" width="900"/>](vignettes/cols4all_fair_sort_cbf.jpg)

@@

[<img src="vignettes/cols4all_div.jpg" width="900"/>](vignettes/cols4all_div.jpg)

@@

[<img src="vignettes/c4a_pals.jpg" width="900"/>](vignettes/c4a_pals.jpg)

@@

[<img src="vignettes/area7.jpg" width="900"/>](vignettes/area7.jpg)

@@

[<img src="vignettes/area7d.jpg" width="900"/>](vignettes/area7d.jpg)

@@

[<img src="vignettes/line7_wt.jpg" width="440"/>](vignettes/line7_wt.jpg)
[<img src="vignettes/line7_bk.jpg" width="440"/>](vignettes/line7_bk.jpg)

@@

[<img src="vignettes/friendly13.jpg" width="900"/>](vignettes/friendly13.jpg)
